---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Introduction
------------------------------------------------------------------------------------------------
This is a package to deal with the data from US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, it can analyse the accident datas from different states in 
different years.

#Functions
------------------------------------------------------------------------------------------------
##make_filename
this function makes the year you want the standard file name for covenience after
```{r make_filename}
make_filename <- function(year) {
  year <- as.integer(year)
  sprintf("accident_%d.csv.bz2", year)}
filename<-make_filename(2014)
print(filename)
```

##fars_read
this function continues the make_filename funtion to read the data according to the years and 
make it data frame.(use the make_filename funciton first.)
```{r fars_read}
fars_read <- function(filename) {
  if(!file.exists(filename))
    stop("file '", filename, "' does not exist")
  data <- suppressMessages({
    readr::read_csv(filename, progress = FALSE)
  })
  dplyr::tbl_df(data)
}
filepath <- system.file("extdata", filename, package = "farsfunctions")
accident_2014 <- fars_read(filepath)
print(head(accident_2014))
```

##fars_read_years
this function will arrange the data by months and years
```{r fars_read_years}

fars_read_years <- function(years) {
        lapply(years, function(year) {
                file <- make_filename(year)
                tryCatch({
                        dat <- fars_read(system.file("extdata", file, package = "farsfunctions"))
                        dplyr::mutate(dat, year = year) %>% 
                                dplyr::select(MONTH, year)
                        }, error = function(e) {
                        warning("invalid year: ", year)
                        return(NULL)
    })
  })
}
accidents <- fars_read_years(2014)
print(accidents)
```

##fars_summarize_years
this function will summarize the total accidents by months and show the spread sheet.
```{r fars_summarize_years}
fars_summarize_years <- function(years) {
  dat_list <- fars_read_years(years)
  dplyr::bind_rows(dat_list) %>%
    dplyr::group_by(year, MONTH) %>%
    dplyr::summarize(n = n()) %>%
    tidyr::spread(year, n)
}
summary <- fars_summarize_years(2013:2015)
print(summary)
```

##fars_map_state
this funtion will show the number of the accident in the year on the map of states
```{r fars_map_state}
fars_map_state <- function(state.num, year) {
  filename <- make_filename(year)
  data <- fars_read(system.file("extdata", file, package = "farsfunctions"))
  state.num <- as.integer(state.num)

  if(!(state.num %in% unique(data$STATE)))
    stop("invalid STATE number: ", state.num)
  data.sub <- dplyr::filter(data, STATE == state.num)
  if(nrow(data.sub) == 0L) {
    message("no accidents to plot")
    return(invisible(NULL))
  }
  is.na(data.sub$LONGITUD) <- data.sub$LONGITUD > 900
  is.na(data.sub$LATITUDE) <- data.sub$LATITUDE > 90
  with(data.sub, {
    maps::map("state", ylim = range(LATITUDE, na.rm = TRUE),
              xlim = range(LONGITUD, na.rm = TRUE))
    graphics::points(LONGITUD, LATITUDE, pch = 46)
  })
}
fars_map_state(1, 2014)
```
